Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-08-31 reanalysis-5-outcome_analysis.qmd
bug fix

  # Get confidence intervals using confint if not present
  if (!("lower.CL" %in% names(contrasts_df))) {
    contrasts_ci <- confint(contrasts_lapse)
    contrasts_df <- cbind(contrasts_df, contrasts_ci[, c("lower.CL", "upper.CL")])
  }

@@

  or_display <- data.frame(
    Contrast = "Lapsed vs Not Lapsed",
    Odds_Ratio = round(or_value, 3),
    SE = round(contrasts_df$SE[1], 4),
    CI_Lower = round(1/contrasts_df$upper.CL[1], 3),  # Invert and swap
    CI_Upper = round(1/contrasts_df$lower.CL[1], 3),  # Invert and swap
    p.value = format.pval(contrasts_df$p.value[1], digits = 4, eps = 0.0001)
  )

>>>>

  # Get confidence intervals using confint if not present
  if (!("lower.CL" %in% names(contrasts_df))) {
    contrasts_ci <- confint(contrasts_lapse)
    contrasts_df <- cbind(contrasts_df, contrasts_ci[, c("asymp.LCL", "asymp.UCL")])
  }

@@

  or_display <- data.frame(
    Contrast = "Lapsed vs Not Lapsed",
    Odds_Ratio = round(or_value, 3),
    SE = round(contrasts_df$SE[1], 4),
    CI_Lower = round(1/contrasts_df$asymp.UCL[1], 3),  # Invert and swap
    CI_Upper = round(1/contrasts_df$asymp.LCL[1], 3),  # Invert and swap
    p.value = format.pval(contrasts_df$p.value[1], digits = 4, eps = 0.0001)
  )
